---
title: "Homwork1 "
author: "Homework01Gr#" #change to your group number
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### NOTE: only those who contributes and fully participates in the work will get credit

**Scribe:**

**Moderator:**

**All contributors:**



## Q1:

The barista at ``t-test espresso'' is told that the optimal serving temperature for coffee is 180 F. Five temperatures are taken of the served coffee: 175, 185, 170, 184, and 175 degrees. 

TASK: Find a 90% confidence interval of the form $(-\infty, b)$ for the mean temperature.(one side CI)

DATA:
```{r}
temp <- c(175, 185, 170, 184, 175)
n <- length(temp)
alpha <- 0.1
x_bar <- mean(temp)
s <- sd(temp)
```

## Part 1

Since the number of samples is not large enough, we calculate the one-sided CI using $t$-distribution:
Type the formula below : The Equation are : 

$ CI_{Upper} = \bar{x} + t_{\alpha}_{df}\frac{s}{sqrt{n}}\$

$ t_{\alpha}_{df} = \frac{\bar{x}-\mu}{\frac{s}{sqrt{n}}}\$

## Part2
Compute one sided CI below

The corresponding t score is:
```{r}
#type codes here
t_score <- qt(1-alpha, n-1);t_score
CI_Upper = x_bar + t_score*(s/sqrt(n));CI_Upper
```

## Part 3
Alternatively, using t.test with alt="less" will give this type of one-sided confidence interval:
```{r}
t.test(temp,alternative = c("less"),conf.level = 0.90)
```

## After class activities (this part is HW2 from the past)
Verzani BOOK,  Problem 3.16,  3.17,  3.31,   8.6,   8.8,   8.12,  8.19: 

##### Probelem : 3.16 :
The data set twins (UsingR) contains IQ scores for pairs of identical twins who were separated at birth. Make a scatter plot of the variables Foster and
Biological. Based on the scatter plot, predict what the Pearson correlation coefficient will be and whether the Pearson and Spearman coefficients will
be similar. Check your guesses.

##Q2  Verzani Problem 3.16
```{r V3.16}
#type codes here
if (!require("UsingR")) 
  install.packages("UsingR") 


data("twins")
plot(twins$Foster, twins$Biological,
     main = "Scatter Plot of Foster vs. Biological IQ Scores",
     xlab = "Foster ",
     ylab = "Biological ",
     pch = 14, col = "red")

pearson_corr <- cor(twins$Foster, twins$Biological, method = "pearson")
cat("Pearson Correlation Coefficient:", round(pearson_corr, 4), "\n")
spearman_corr <- cor(twins$Foster, twins$Biological, method = "spearman")
cat("Spearman Correlation Coefficient:", round(spearman_corr, 4), "\n")

```
### Probelm 3.17 : 
The state.x77 data set contains various information for each of the fifty United States. We wish to explore possible relationships among the variables. First, we make the data set easier to work with by turning it into a data frame.
##Q3  Verzani Problem 3.17
```{r V3.17}
#type codes here
if (!require("HistData")) 
  install.packages("HistData")

data("coins")
state_data <- as.data.frame(state.x77)


cat("Dataset Dimensions (Rows x Columns):", dim(state_data), "\n")
cat("Column Names:", colnames(state_data), "\n")
colnames(state_data) <- make.names(colnames(state_data))

column_lengths <- sapply(state_data, length)
if (!all(column_lengths == 50)) {
    stop("ERROR: Some columns do not have exactly 50 rows. Check dataset integrity!")
}

plot(state_data$Frost, state_data$Population,
     main = "Population vs. Frost",
     xlab = "Frost (Avg Days Below Freezing)",
     ylab = "Population",
     pch = 16, col = "blue")

plot(state_data$Population, state_data$Murder,
     main = "Murder Rate vs. Population",
     xlab = "Population",
     ylab = "Murder Rate",
     pch = 16, col = "red")

plot(state_data$Area, state_data$Population,
     main = "Population vs. Area",
     xlab = "Area (sq miles)",
     ylab = "Population",
     pch = 16, col = "green")

plot(state_data$HS.Grad, state_data$Income,  
     main = "Income vs. High School Graduation Rate",
     xlab = "High School Graduation Rate (%)",
     ylab = "Income",
     pch = 16, col = "purple")

```
### Problem 4 : 
3.31 The data set coins (UsingR) contains the number of coins in a change
bin and the years they were minted. Do the following:
1. How much money is in the change bin?
2. Make a barplot of the years. Is there a trend?
3. Use cut to construct a barplot by decade.
4. Make a contingency table of the year and the value. Does it look like
the two variables are associated? Why?

##Q4  Verzani Problem 3.31
```{r V3.31}
#type codes here
if (!require("UsingR")) install.packages("UsingR")
if (!require("HistData")) install.packages("HistData")
library(UsingR)
library(HistData)

knitr::opts_chunk$set(echo = TRUE)

data("coins")
head(coins)

# part 1
total_money <- sum(coins$value)
cat("The Money change bin: $", total_money, "\n")

# part 2
barplot(table(coins$year),
        main = "Frequency by Year",
        xlab = "Year",
        ylab = "Count",
        col = "blue")

# part 3
coins$decade <- cut(coins$year, breaks = seq(1900, 2020, by = 10), right = FALSE)

barplot(table(coins$decade),
        main = "Coins by Decade",
        xlab = "Decade",
        ylab = "Count",
        col = "red")

# part 4
contingency_table <- table(coins$year, coins$value)
print(contingency_table)

```

### Problem 8.6: 
A student wishes to find the proportion of left-handed people at her college. She surveys 100 fellow students and finds that only 5 are left-handed.
If she computed a 95% confidence interval would it contain the value of p = 1/10? 

## For solution we need blow Equations : 
\[
CI = \hat{p} \pm Z_{\alpha/2} \times \sqrt{\frac{\hat{p} (1 - \hat{p})}{n}}
\]

##Q5  Verzani Problem 8.6
```{r V8.6}
#type codes here
x <- 5    
n <- 100
z_value= qnorm(0.975)  
p_hat <- x / n
CI <- c(p_hat - z_value * sqrt(p_hat * (1 - p_hat) / n), 
        p_hat + z_value * sqrt(p_hat * (1 - p_hat) / n))

cat("p_hat:", p_hat, "\n")
cat("Z-value:", z_value, "\n")
cat("95% CI: [", CI[1], ",", CI[2], "]\n")

#  Check The conditions :  if p = 0.1 
p_test <- 0.1  
if (CI[1] <= p_test && p_test <= CI[2]) {
  cat("The CI contains p = 0.1\n")
} else {
  cat("The CI does NOT contain p = 0.1\n")
}


```
### Problem 8.8: 
A New York Times article from October 9, 2003, contains this explanation  about an exit survey for a California recall election:
In theory, in 19 cases out of 20, the results from such polls should differ by no more than plus or minus two percentage points from what would have been obtained by seeking to interview everyone who cast a ballot in the recall election.
Assume a simple random sample and bp = .54. How big was n?.

####For soltion we are using blow equation: 

\[
n = \left( \frac{Z \times \sqrt{\hat{p}(1 - \hat{p})}}{ME} \right)^2
\]


##Q6  Verzani Problem 8.8
```{r V8.8}
#type codes here
ME = 0.02           
p_hat = 0.54        
z_value = 1.96      
n = (z_value^2 * p_hat * (1 - p_hat)) / (ME^2)

cat("Required sample size of (n):", ceiling(n), "\n")

```
##Q7  Verzani Problem 8.12
The phrasing, “The true value, p, is in the confidence interval with 95% probability” requires some care. Either p is or isn’t in a given interval. What
it means is that if we repeated the sampling, there is a 95% chance the true value is in the random interval. We can investigate this with a simulation.
The commands below will find several confidence intervals at once.

## We are going to used blow Equations: 

\[
CI = \hat{p} \pm Z \times \sqrt{\frac{\hat{p} (1 - \hat{p})}{n}}
\]

##Q7  Verzani Problem 8.12
```{r V8.12}
#type codes here: 
M <- 50              
n <- 2              
p <- 0.5            
alpha <- 0.05        

zstar <- qnorm(1 - alpha / 2)
phat <- rbinom(M, n, p) / n
SE <- sqrt(phat * (1 - phat) / n)

Lp <- phat - zstar * SE
Up <- phat + zstar * SE

RR <- ((sum(lower_bound < p & p < upper_bound))/M) *100

cat("% CI - containing p:", RR, "%\n")
matplot(rbind(Lp, Up), rbind(1:M, 1:M), type = "l", lty = 1,
        xlab = "CI", ylab = "Simulation Number")

abline(v = p, col = "blue", lwd = 2, lty = 2)  

```
## Problem 8.19 : 
The t-distribution is also called the Student t-distribution. A Guinness Brewery employee, William Gosset, derived the distribution of T to handle
small samples. (Large samples of beer presumably led to less publishable science.) As Guinness did not allow publication of research results at the
time, Gosset chose to publish under the pseudonym Student. The journal chosen was Pearson’s journal, a colleague of Gosset and pioneer of statistics.
Gosset applied his research to a data set containing height and leftmiddle- finger measurements of 3,000 criminals. These values were written
on cards and randomly sorted into 750 samples, each containing four crimi8.2. CONFIDENCE INTERVALS FOR THE POPULATION MEAN 277 nals. (This is how simulations were done previously.) The data is available in the Macdonell (HistData) data set. Run a simulation using 750 samples of size 4. Use quantile to find a 95% confidence interval. Compare to that found with t.test for a single sample of size 4. As the data is tabulated, you’ll need to expand it:

### Equations: 
\[
CI = \bar{x} \pm t_{\alpha/2, \, df} \times \left(\frac{s}{\sqrt{n}}\right)
\]


##Q8  Verzani Problem 8.19
```{r V8.19}
#type codes here
require(HistData)
finger <- with(Macdonell, rep(finger, frequency))
res <- replicate(750, mean(sample(finger, 4, replace = TRUE)))
quantile(res, c(0.025, 0.975))
cat("\n")  

n <- 4
x <- sample(finger, n, replace = TRUE)
t.test(x, conf.level = 0.95)$conf.int
cat("\n")  
```
#######

Devore BOOK : section 7.2 problem 16; Sec 7.3: problem 32
### Problem : 16.: 
The alternating current (AC) breakdown voltage of an insulating liquid indicates its dielectric strength. The article “Testing Practices for the AC Breakdown Voltage Testing of Insulation Liquids” (IEEE Electrical Insulation Magazine, 1995: 21–26) gave the accompanying sample observations on breakdown voltage (kV) of a particular circuit under certain conditions.

62 50 53 57 41 53 55 61 59 64 50 53 64 62 50 68
54 55 57 50 55 50 56 55 46 55 53 54 52 47 47 55
57 48 63 57 57 55 53 59 53 52 50 55 60 50 56 58 .

### Equation : 
\[
CI = \bar{x} \pm t_{\alpha/2} \times \left(\frac{s}{\sqrt{n}}\right)
\]

##Q9  Devore BOOKProblem 3.16
```{r V9}
#type codes here
### part A
# breakdown voltage data
voltage_data <- c(62, 50, 53, 57, 41, 53, 55, 61, 59, 64, 50, 53, 64, 62, 50, 68,
                  54, 55, 57, 50, 55, 50, 56, 55, 46, 55, 53, 54, 52, 47, 47, 55,
                  57, 48, 63, 57, 57, 55, 53, 59, 53, 52, 50, 55, 60, 50, 56, 58)
summary(voltage_data)

# part B
boxplot(voltage_data, main = "plots Breakdown Voltage (kV)",
        xlab = "Breakdown Voltage (kV)", col = "lightblue", horizontal = TRUE)

outliers <- boxplot.stats(voltage_data)$out
cat("Potential Outliers:", outliers, "\n")

# part B
sample_mean <- mean(voltage_data)
sample_sd <- sd(voltage_data)
       
n = 48                   
t_value = 1.96          

SE = sd / sqrt(n)
CI_lower = mean - t_value * SE
CI_upper = mean + t_value * SE

cat("95% CI Breakdown Voltage: [", 
    round(CI_lower, 1), ",", round(CI_upper, 1), "]\n")

# Part D
margin_error = 1       
a_sd = 7.5               
t_value = 1.96                

required_n = (t_value * a_sd / margin_error)^2
required_n = (required_n)  # Round up to nearest whole number

cat("Required Sample Size for Desired Precision (E = 1 kV):", required_n, "\n")


```
##### 32 
According to the article “Fatigue Testing of Condoms” (Polymer Testing, 2009: 567–571), “tests currently used for condoms are surrogates for the challenges they face in use,” including a test for holes, an inflation test, a package seal test, and tests of dimensions and lubricant quality (all
fertile territory for the use of statistical methodology!). The investigators developed a new test that adds cyclic strain to a level well below breakage and determines the number of cycles to break. A sample of 20 condoms of one particular type resulted in a sample mean number of 1584 and a
sample standard deviation of 607. Calculate and interpret a confidence interval at the 99% confidence level for the true average number of cycles to break. [Note: The article presented the results of hypothesis tests based on the t distribution; the validity of these depends on assuming normal population distributions.

### Equation are used : 
The t-distribution is used because the population standard deviation is unknown, and the sample size is small (\(n < 30\)).
\[
CI = \bar{x} \pm t_{\alpha/2} \times \left(\frac{s}{\sqrt{n}}\right)
\]
Where:
The \( t_{\alpha/2} \) is the critical t-value for a 99% confidence level with df = n - 1 degrees of freedom. and  \( \frac{s}{\sqrt{n}} \) is the standard error of the mean.

##Q10  Devore BOOK Problem 32

```{r V32}
#type codes here
n = 20
mean = 1584
sd = 607
con_level = 0.99
alpha = 1 - con_level
t_value <- qt(1 - alpha/2, df = n - 1)
CI_l <- mean - t_value * (sd / sqrt(n))
CI_u <- mean + t_value * (sd / sqrt(n))

cat("CI- Mean: [", 
    round(CI_l, 1), ",", round(CI_u, 1), "]\n")

```